### 2016-08-31 version0.0/intro0.01.tex
Changing plots in ch4. to flux density instead of flux

\hii~regions are hot and low density regions that are mostly located in the disks of spiral galaxies.
High energy UV photons emitted by massive new born stars have sufficient energy to ionize their surrounding gas, and
~\halpha emission is the main observable feature of \hii~regions.
The temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, and forbidden lines such as \sii, \oii, \oiii, and \nii. 
Forbidden lines are not called so because there is no chance of them occurring, but merely because their probability is much lower than the normal ``allowed'' transitions.
Optically bright \halpha emission from \hii~regions is correlated with number of new massive stars in regions, and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
Studying \hii~regions provides valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and empirically found to have a power-law size distribution.
The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\citep{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).

@@

\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is:
\begin{equation}
L_{CO} = D^2 \int I_{\rm CO} d\Omega, 
\end{equation}
%NOTE: Equations must be punctuated.%
where $D$ is the distance to the cloud and $I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in K~km~s$^{-1}$.
It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(K) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$.
For a uniform cloud with a radius $R$, the CO luminosity is given by:
 \begin{equation}
L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V.
\end{equation}

@@

Atomic gas in galaxies is dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-2}$), along the line-of-sight.
\begin{equation}
N_{H {\sc I}}  \propto \int T_{\mathrm B} dV
\end{equation}
where $T_{\mathrm B}$ is the temperature brightness in Kelvin and dV is in km~s$^{-1}$, with the integral over the line profile. 
These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi~is detectable in most spiral galaxies and some elliptical galaxies).
Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.

@@

Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to low spatial resolution of available observational data.
\cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin. 
The Herschel Space Telescope~\citep{Pilbratt10} has measured the continuum dust emission from hundreds of galaxies~\citep{Eales10, Oliver12}. 
This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
The observed FIR flux has almost no dependency on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary. 
The other important advantage is that this method solves the newly-found problem of ``dark gas" in galaxies. 
Dark gas is a significant fraction of gas in galaxies which can be traced by neither the 21-cm emission nor the CO emission~\citep{Abdo10}. 
As such, it is very difficult to detect with telescopes, but an accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.

@@

In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission. 
Some of this emission is directly from stars, e.g.\ UV emission, and some is from ISM components that absorb and re-emit light from young stars, e.g.\ far-infrared emission.
Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}. 
Peak of emission of young, hot, and massive stars is in UV wavelength, which makes them an ideal tracer of the current SFR.
One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. 
By knowing the IMF, the number of massive stars can be used to extrapolate the total number of stars formed in a given star-forming region.
To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Section~\ref{sec: imf}).
In general each tracer has some systematic errors, and one should decide which tracer is more accurate for a given system.

@@

In the late 1970s, it was recognised that the assumption of a the single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}. 
Since then, many groups have studied the stellar IMF and found different power-law relations (Fig.~\ref{fig: imf} ). 
Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\ \cite{Kroupa01}:
\begin{equation}
\begin{split}
    \Phi (\log M) & \propto M^{-2.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
           & \propto M^{-3.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
\end{split}
\end{equation}
Although the Salpeter IMF produces more low-mass stars than the Kroupa IMF, they produce almost the same number of high-mass stars. 
Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF can be converted to the Salpeter IMF by multiplying the calibration constant by 0.67~\citep{Madau14}.
In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars with masses greater than 8M$_\odot$.
\cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high-mass end.

\begin{figure}
\centering
\includegraphics[width=15.5cm]{../image_intro/imf.png}
\small
\caption[Comparing stellar initial mass functions]{Comparing stellar initial mass functions (IMFs) by plotting the mass fraction per dex, power of 10, versus mass, normalized so that the integral under each curve is unity. The mass ranges from 0.1 to 120~M$_\odot$. Adopted from~\cite{Baldry03}.} 
\label{fig: imf}
\end{figure}

@@

\subsubsection{Resolved Star Formation Indicators}
The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
These objects mostly few million years old and usually are referred to as young stellar objects (YSOs). 
Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$~kpc of the Solar System. 
The number of YSOs can be converted to SFR using: 
\begin{equation}
{\m SFR}(YSO) = N_{yso} <M>/\tau 
\end{equation}
where SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$, N$_{yso}$ is the number of YSOs.
$<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
$\tau$ is the lifetime of the YSO  $\tau \sim 2$~Myr~\citep{Evans09}. 
Since our current devices cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.

@@

In order to derive conversions between the luminosity in specific wavelengths and the SFR, stellar population synthesis models are used~\citep{Kennicutt98b}. 
The general form of a SFR calibration using single-band emission is: 
\begin{equation}
\label{equ: sfrsingle}
{\rm SFR}(\lambda)= CL(\lambda),
\end{equation}
where SFR is in units of M${_\odot}$~yr$^{-1}$, $L(\lambda)$ is the luminosity in erg~s$^{-1}$ at the wavelength $\lambda$, and $C$ is a constant derived from stellar population models~\citep[e.g, starburst99][]{Leitherer99}). 
The constant $C$ varies for different wavelengths, mass ranges of the stellar IMF, and the timescale $\tau$ over which star formation is assumed to remain constant. 
Table~\ref{table1}, from \cite{Calzetti13}, summarises some values of $C$ and their changes according to different assumptions about the IMF.

\begin{table}
\caption{Luminosity-to-SFR calibrations adapted from~\cite{Calzetti13}}
\label{table1}
\begin{center}
\begin{tabular}{ c c c }
\hline\hline
Luminosity$^1$ & C$^2$ & Assumptions$^3$\\
\hline
L$_{UV}$ & $3.0 \times 10^{(-47)} \lambda$ &$0.1 -100 M_{\odot}, \tau \ge 100 Myr $\\
L$_{UV}$ & $4.2 \times 10^{(-47)} \lambda$ &$0.1 -30 M_{\odot}, \tau \ge 100 Myr $\\
L$_{UV}$ & $4.3 \times 10^{(-47)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 10 Myr $\\
L$_{UV}$ & $1.0 \times 10^{(-46)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $1.6 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $2.8 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $4.1 \times 10^{(-44)}$ &$0.1 -30 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $3.7 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $8.3 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(H${\alpha}$) & $5.5 \times 10^{(-42)}$&$0.1 -100 M_{\odot},  \tau \ge 6 Myr $\\
L(H${\alpha}$) & $3.1 \times 10^{(-41)}$&$0.1 -30 M_{\odot},  \tau \ge 10 Myr $\\
\hline
\end{tabular}
\end{center}
\begin{tablenotes}
\item $^1$ Luminosities (except for UV) are in erg~s$^{-1}$ and are given as $\nu L_{\nu}$.
\item $^2$ The constant $C$ appears in Equ.~\ref{equ: sfrsingle}. For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in \AA to convert luminosity density to luminosity. 
\item $^3$ Assumptions for the mass range of the stellar IMF, using the expression derived by \cite{Kroupa01} (see Section~\ref{sec: imf}), and for the timescale $\tau$.
\end{tablenotes}
\end{table}

@@

Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727~\AA. 
Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. 
\cite{Gallagher89} calibrated the SFR based on the \oii~luminosity by using a sample of 75 galaxies. 
Another calibration for this luminosity was derived by \cite{Kennicutt92}. 
In his review on the SFR,~\citep{Kennicutt98b} averaged these calibrations and derived the following relation:
\begin{equation}
SFR([O\ II]) = 1.4 \times 10^{-41} L([O\ II])
\end{equation}  
where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high-redshift galaxies.
In these galaxies, the \halpha emission line is redshifted out of the optical band.
Consequently, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is very useful~\citep{Kennicutt98b}.

@@

TIR luminosity can be measured from the integrated infrared SED or a calibration of spatially-resolved infrared photometry introduced by~\cite{Draine07}. 
\cite{Boquien10} modified calibration of the total infrared luminosity as: 
\begin{equation}
L(\rm TIR) = 0.95L(PAH 8 \mu m) + 1.15L(24 \mu m) + L(70 \mu m) + L(160 \mu m),
\end{equation}
where $L = \nu L_{\nu}$ is the luminosity in erg~s$^{-1}$ at frequency $\nu$. 
\cite{Calzetti07} indicated that the star formation rate calibration for a stellar population undergoing constant star formation over $\tau=$100~Myr is:
\begin{equation}
\label{sfr_tot_IR}
SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR),
\end{equation}
where SFR(TIR) is in M${\odot}$~yr$^{-1}$, and L(TIR) is in erg~s$^{-1}$.

@@

\begin{table}
\caption{SFR calibrations from PAH luminosities; adopted from~\cite{Shipley16}}
\label{table_PAH}
\begin{center}
\begin{tabular}{ l c c}
\hline\hline
PAH Feature(s) & A & B\\
\hline
6.2 + 7.7 + 11.3 & $ -42.56 \pm 0.03 $ &  $1.00 \pm 0.03$ \\ 
6.2 & $ -40.06 \pm 0.09 $ &  $0.96 \pm 0.04$ \\ 
7.7 & $ -42.38 \pm 0.06 $ &  $1.00 \pm 0.03$ \\ 
11.3 & $ -44.14 \pm 0.08 $ &  $1.06 \pm 0.03$ \\ 
6.2 + 7.7 & $ -42.05 \pm 0.04 $ &  $0.99 \pm 0.03$ \\ 
6.2 + 11.3 & $ -42.52 \pm 0.05 $ &  $1.01 \pm 0.03$ \\ 
7.7 + 11.3 & $ -42.85 \pm 0.04 $ &  $1.01 \pm 0.03$ \\ 
\hline
\end{tabular}
\end{center}
\end{table}

The most common use of combining luminosities to trace the SFR is the combination of total infrared measurements with both far- and near-ultraviolet observations, with the latter being more commonly used. 
This combination helps to avoid uncertainties from corrections for dust attenuation in far-UV (FUV) observations~\citep[e.g.][]{Hao11}. The calibration is:
\begin{equation}
L_{FUV}(\rm corr) = L_{FUV}(\rm obs) + \alpha L_{\rm TIR},
\end{equation}
where the luminosities are $L = \nu L_{\nu}$ in erg~s$^{-1}$, and the coefficient $\alpha$ depends on the bandpasses chosen for the UV and IR measurements. $\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies are from dust heated by older populations of stars~\citep{Kennicutt12}. The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs~\citep[e.g.][]{Hao11, Leroy08}.

@@

\begin{table}
\caption{Multi-wavelength dust-corrected luminosities, adopted from~\cite{Kennicutt12}}
\label{table3}
\begin{center}
\begin{tabular}{ c}
\hline\hline
Combined luminosities$^1$ \\
\hline
L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)$^2$\\
L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)$^2$\\
L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 0.27L(TIR)$^2$\\
L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 2.26L(24~$\mu$m)$^2$\\
L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.0024L(TIR)$^3$\\
L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.020L(24~$\mu$m)$^3$\\
\hline
\end{tabular}
\end{center}
\begin{tablenotes}
\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L$_{\lambda}$ in erg~s$^{-1}$ 
\item $^2$ Calibrated by~\cite{Hao11}
\item $^3$ Calibrated by~\cite{Kennicutt09}
\end{tablenotes}
\end{table}

>>>>

\hii~regions are hot and low density regions that are mostly located in the disks of spiral galaxies.
High energy UV photons emitted by massive new born stars have sufficient energy to ionize their surrounding gas, and
~\halpha emission is the main observable feature of \hii~regions.
The temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, and forbidden lines such as \sii, \oii, \oiii, and \nii. 
Forbidden lines are not called so because there is no chance of them occurring, but merely because their probability is much lower than the normal ``allowed'' transitions.
Optically bright \halpha emission from \hii~regions is correlated with the number of new massive stars in regions, and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
Studying \hii~regions provides valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and empirically found to have a power-law size distribution.
The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar populations~\citep{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).

@@

\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is:
\begin{equation}
L_{CO} = D^2 \int I_{\rm CO} d\Omega, 
\end{equation}
%NOTE: Equations must be punctuated.%
where $D$ is the distance to the cloud and $I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in K~km~s$^{-1}$.
It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(K) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$. %PB: please check this: I think \int should be omitted, dV should be \Delta V, and $V$ should also be $\Delta V$
For a uniform cloud with a radius $R$, the CO luminosity is given by:
 \begin{equation}
L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V.
\end{equation}

@@

Atomic gas in galaxies is dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-2}$), along the line-of-sight.
\begin{equation}
N_{H {\sc I}}  \propto \int T_{\mathrm B} dV
\end{equation}
where $T_{\mathrm B}$ is the brightness temperature  in Kelvin and $dV$ is in km~s$^{-1}$, with the integral over the line profile. 
These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi~is detectable in most spiral galaxies and some elliptical galaxies).
Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.

@@

Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to the low spatial resolution of available observational data.
\cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin. 
The Herschel Space Telescope~\citep{Pilbratt10} has measured the continuum dust emission from hundreds of galaxies~\citep{Eales10, Oliver12}. 
This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
The observed FIR flux has almost no dependency on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary. 
The other important advantage is that this method solves the newly-found problem of ``dark gas" in galaxies. 
Dark gas is a significant fraction of gas in galaxies which can be traced by neither the 21-cm emission nor the CO emission~\citep{Abdo10}. 
As such, it is very difficult to detect with telescopes, but an accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.

@@

In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission. 
Some of this emission is directly from stars, e.g.\ UV emission, and some is from ISM components that absorb and re-emit light from young stars, e.g.\ far-infrared emission.
Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}. 
The peak of emission of young, hot, and massive stars is at UV wavelengths, which makes them an ideal tracer of the current SFR.
One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. 
By knowing the IMF, the number of massive stars can be used to extrapolate the total number of stars formed in a given star-forming region.
To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Section~\ref{sec: imf}).
In general each tracer has some systematic errors, and one should decide which tracer is more accurate for a given system.

@@

In the late 1970s, it was recognised that the assumption of a the single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}. 
Since then, many groups have studied the stellar IMF and found different power-law relations (Fig.~\ref{fig: imf} ). 
Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\ \cite{Kroupa01}:
\begin{equation}
\begin{split}
    \Phi (\log M) & \propto M^{-2.3}    \quad    (0.1 \le M(M_{\odot}) \le 0.5)\\                  
           & \propto M^{-3.3}    \quad    (0.5 \le M(M_{\odot}) \le 100)
\end{split}
\end{equation}
Although the Salpeter IMF produces more low-mass stars than the Kroupa IMF, they produce almost the same number of high-mass stars. 
Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF can be converted to the Salpeter IMF by multiplying the calibration constant by 0.67~\citep{Madau14}.
In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars with masses greater than 8M$_\odot$.
\cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high-mass end.

\begin{figure}
\centering
\includegraphics[width=15.5cm]{../image_intro/imf.png}
\small
\caption[Comparing stellar initial mass functions]{Comparing stellar initial mass functions (IMFs) by plotting the mass fraction per dex, power of 10, versus mass, normalized so that the integral under each curve is unity. The mass ranges from 0.1 to 120~M$_\odot$. Adapted from~\cite{Baldry03}.} 
\label{fig: imf}
\end{figure}

@@

\subsubsection{Resolved Star Formation Indicators}
The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
These objects mostly few million years old and usually are referred to as young stellar objects (YSOs). 
Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$~kpc of the Solar System. 
The number of YSOs can be converted to SFR using: 
\begin{equation}
{\m SFR}(YSO) = N_{yso} <M>/\tau 
\end{equation}
where SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$, N$_{yso}$ is the number of YSOs.
$<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
$\tau$ is the lifetime of the YSO,  $\tau \sim 2$~Myr~\citep{Evans09}. 
Since our current devices cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.

@@

In order to derive conversions between the luminosity in specific wavelengths and the SFR, stellar population synthesis models are used~\citep{Kennicutt98b}. 
The general form of a SFR calibration using single-band emission is: 
\begin{equation}
\label{equ: sfrsingle}
{\rm SFR}(\lambda)= CL(\lambda),
\end{equation}
where SFR is in units of M${_\odot}$~yr$^{-1}$, $L(\lambda)$ is the luminosity in erg~s$^{-1}$ at the wavelength $\lambda$, and $C$ is a constant derived from stellar population models~\citep[e.g., Starburst99][]{Leitherer99}). 
The constant $C$ varies for different wavelengths, mass ranges of the stellar IMF, and the timescale $\tau$ over which star formation is assumed to remain constant. 
Table~\ref{table1}, from \cite{Calzetti13}, summarises some values of $C$ and their changes according to different assumptions about the IMF.

\begin{table}
\caption{Luminosity-to-SFR calibrations adapted from~\cite{Calzetti13}}
\label{table1}
\begin{center}
\begin{tabular}{ c c c }
\hline\hline
Luminosity$^1$ & C$^2$ & Assumptions$^3$\\
\hline
L$_{UV}$ & $3.0 \times 10^{(-47)} \lambda$ &$0.1 -100 M_{\odot}, \tau \ge 100$ Myr \\
L$_{UV}$ & $4.2 \times 10^{(-47)} \lambda$ &$0.1 -30 M_{\odot}, \tau \ge 100$ Myr \\
L$_{UV}$ & $4.3 \times 10^{(-47)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 10$ Myr \\
L$_{UV}$ & $1.0 \times 10^{(-46)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 100$ Myr \\
L(TIR) & $1.6 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100$Myr \\
L(TIR) & $2.8 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100$ Myr \\
L(TIR) & $4.1 \times 10^{(-44)}$ &$0.1 -30 M_{\odot}, \tau = 100$ Myr \\
L(TIR) & $3.7 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100$ Myr \\
L(TIR) & $8.3 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100$ Myr \\
L(H${\alpha}$) & $5.5 \times 10^{(-42)}$&$0.1 -100 M_{\odot},  \tau \ge 6$ Myr \\
L(H${\alpha}$) & $3.1 \times 10^{(-41)}$&$0.1 -30 M_{\odot},  \tau \ge 10$ Myr \\
\hline
\end{tabular}
\end{center}
\begin{tablenotes}
\item $^1$ Luminosities (except for UV) are in erg~s$^{-1}$ and are given as $\nu L_{\nu}$.
\item $^2$ The constant $C$ appears in Equ.~\ref{equ: sfrsingle}. For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in \AA to convert luminosity density to luminosity. 
\item $^3$ Assumptions for the mass range of the stellar IMF, using the expression derived by \cite{Kroupa01} (see Section~\ref{sec: imf}), and for the timescale $\tau$.
\end{tablenotes}
\end{table}

@@

Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727~\AA. 
Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. 
\cite{Gallagher89} calibrated the SFR based on the \oii~luminosity by using a sample of 75 galaxies. 
Another calibration for this luminosity was derived by \cite{Kennicutt92}. 
In his review on the SFR,~\citep{Kennicutt98b} averaged these calibrations and derived the following relation:
\begin{equation}
SFR([O\ II]) = 1.4 \times 10^{-41} L([O\ II])
\end{equation}  
where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
Although SFR(\oii) is not as accurate as the SFR(\halphafot), it is one of major SFR indicators in high-redshift galaxies.
In these galaxies, the \halpha emission line is redshifted out of the optical band.
Consequently, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is very useful~\citep{Kennicutt98b}.

@@

TIR luminosity can be measured from the integrated infrared SED or a calibration of spatially-resolved infrared photometry introduced by~\cite{Draine07}. 
\cite{Boquien10} modified calibration of the total infrared luminosity as: 
\begin{equation}
L(\rm TIR) = 0.95L(PAH 8 \mu m) + 1.15L(24 \mu m) + L(70 \mu m) + L(160 \mu m),
\end{equation}
where $L = \nu L_{\nu}$ is the luminosity in erg~s$^{-1}$ at frequency $\nu$. 
\cite{Calzetti07} indicated that the star formation rate calibration for a stellar population undergoing constant star formation over $\tau=$100~Myr is:
\begin{equation}
\label{sfr_tot_IR}
SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR),
\end{equation}
where SFR(TIR) is in M$_{\odot}$~yr$^{-1}$, and L(TIR) is in erg~s$^{-1}$.

@@

\begin{table}
\caption{SFR calibrations from PAH luminosities; adapted from~\cite{Shipley16}}
\label{table_PAH}
\begin{center}
\begin{tabular}{ l c c}
\hline\hline
PAH Feature(s) & A & B\\
\hline
6.2 + 7.7 + 11.3 & $ -42.56 \pm 0.03 $ &  $1.00 \pm 0.03$ \\ 
6.2 & $ -40.06 \pm 0.09 $ &  $0.96 \pm 0.04$ \\ 
7.7 & $ -42.38 \pm 0.06 $ &  $1.00 \pm 0.03$ \\ 
11.3 & $ -44.14 \pm 0.08 $ &  $1.06 \pm 0.03$ \\ 
6.2 + 7.7 & $ -42.05 \pm 0.04 $ &  $0.99 \pm 0.03$ \\ 
6.2 + 11.3 & $ -42.52 \pm 0.05 $ &  $1.01 \pm 0.03$ \\ 
7.7 + 11.3 & $ -42.85 \pm 0.04 $ &  $1.01 \pm 0.03$ \\ 
\hline
\end{tabular}
\end{center}
\end{table}

The most common use of combined luminosities to trace the SFR is the combination of total infrared measurements with both far- and near-ultraviolet observations, with the latter being more commonly used. 
This combination helps to avoid uncertainties from corrections for dust attenuation in far-UV (FUV) observations~\citep[e.g.][]{Hao11}. The calibration is:
\begin{equation}
L_{FUV}(\rm corr) = L_{FUV}(\rm obs) + \alpha L_{\rm TIR},
\end{equation}
where the luminosities are $L = \nu L_{\nu}$ in erg~s$^{-1}$, and the coefficient $\alpha$ depends on the bandpasses chosen for the UV and IR measurements. $\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies are from dust heated by older populations of stars~\citep{Kennicutt12}. The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs~\citep[e.g.][]{Hao11, Leroy08}.

@@

\begin{table}
\caption{Multi-wavelength dust-corrected luminosities, adapted from~\cite{Kennicutt12}}
\label{table3}
\begin{center}
\begin{tabular}{ c}
\hline\hline
Combined luminosities$^1$ \\
\hline
L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)$^2$\\
L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)$^2$\\
L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 0.27L(TIR)$^2$\\
L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 2.26L(24~$\mu$m)$^2$\\
L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.0024L(TIR)$^3$\\
L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.020L(24~$\mu$m)$^3$\\
\hline
\end{tabular}
\end{center}
\begin{tablenotes}
\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L$_{\lambda}$ in erg~s$^{-1}$ 
\item $^2$ Calibrated by~\cite{Hao11}
\item $^3$ Calibrated by~\cite{Kennicutt09}
\end{tablenotes}
\end{table}
